Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-04-12 manuscript/manuscript.tex
ms updates

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-2.pdf}

  \caption{{\bf A}: The convergence correlation, averaged across
    \textcite{Barghi2019-qy} replicate pairs, through time. Each line
    represents the convergence correlation $\mathrm{cor}(\Delta p_{s}, \Delta
    p_{s})$ from a starting reference generation $s$ to a later time $t$, which
    varies along the x-axis; each line corresponds to a row of the temporal
    convergence correlation matrix depicted to the right.  We note that
    convergent correlation for the last timepoint is an outlier; we are unsure
    as to the cause of this, e.g. it does not appear to be driven by a single
    pair of replicates. {\bf B}: The convergence covariance between individual
    pairs of replicates in the \textcite{Kelly2019-dc} data. {\bf C}:  The
    convergence covariance between individual pairs of replicates in
    \parencite{Castro2019-uk} data, for the two selection lines  (LS1 and LS2)
    and the control (Ctrl); gray CIs are those using the complete dataset, blue
  CIs exclude chromosomes 5 and 10 which harbor the two regions
\textcite{Castro2019-uk} found to have signals of parallel selection between
LS1 and LS2.}

>>>>

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-2-revision.pdf}

  \caption{{\bf A}: The convergence \vb{correlations}, averaged across
    \textcite{Barghi2019-qy} replicate pairs, through time. Each line
    represents the convergence correlation $\mathrm{cor}(\Delta p_{s}, \Delta
    p_{s})$ from a starting reference generation $s$ to a later time $t$, which
    varies along the x-axis; each line corresponds to a row of the temporal
    convergence correlation matrix depicted to the right. We note that
    convergent correlation for the last timepoint is an outlier; we are unsure
    as to the cause of this, e.g. it does not appear to be driven by a single
    pair of replicates. {\bf B}: The convergence \vb{correlations} between
    individual pairs of replicates in the \textcite{Kelly2019-dc} data
    (\vb{note the confidence intervals are plotted, but are small on this
    y-axis scale; see note XXX}). {\bf C}:  The convergence \vb{correlations}
    between individual pairs of replicates in \parencite{Castro2019-uk} data,
    for the two selection lines  (LS1 and LS2) and the control (Ctrl); gray CIs
    are those using the complete dataset, blue CIs exclude chromosomes 5 and 10
    which harbor the two regions \textcite{Castro2019-uk} found to have signals
  of parallel selection between LS1 and LS2.}
